Case Study: Gene Set Enrichment Analysis (GSEA), Mouse

### 2018-02-23 datasets/GSEA/gsea-human.Rmd
Fix typo in save file name

```{r goseq, message=FALSE}
goset_data <- file.path(datdir, "goSets.RData")
if (!file.exists(goset_data)) {
    mart <- useMart("ensembl", "hsapiens_gene_ensembl")
    goSets <- getBM( c("ensembl_gene_id", "go_id"), mart = mart,
                    filters = "ensembl_gene_id", values = rownames(res))
    goSets <- goSets[!nchar( goSets$go_id ) == 0, ]
    goSets <- with(goSets, split(go_id, ensembl_gene_id))
    save(goSets, file = file)
} else {
    load(goset_data)
}

>>>>

```{r goseq, message=FALSE}
goset_data <- file.path(datdir, "goSets.RData")
if (!file.exists(goset_data)) {
    mart <- useMart("ensembl", "hsapiens_gene_ensembl")
    goSets <- getBM( c("ensembl_gene_id", "go_id"), mart = mart,
                    filters = "ensembl_gene_id", values = rownames(res))
    goSets <- goSets[!nchar( goSets$go_id ) == 0, ]
    goSets <- with(goSets, split(go_id, ensembl_gene_id))
    save(goSets, file = goset_data)
} else {
    load(goset_data)
}

### 2018-02-23 datasets/GSEA/gsea-mouse.Rmd
Fix typo in save file name

```{r goseq, message=FALSE}
goset_data <- file.path(datdir, "goSetsMm.RData")
if (!file.exists(goset_data)) {
    mart <- useMart("ensembl", "mmusculus_gene_ensembl")
    goSets <- getBM(c("ensembl_gene_id", "go_id"), mart = mart,
                    filters = "ensembl_gene_id", values = rownames(res))
    goSets <- goSets[!nchar(goSets$go_id) == 0, ]
    goSets <- with(goSets, split(go_id, ensembl_gene_id))
    save(goSets, file = file)
} else {
   load(goset_data)
}

>>>>

```{r goseq, message=FALSE}
goset_data <- file.path(datdir, "goSetsMm.RData")
if (!file.exists(goset_data)) {
    mart <- useMart("ensembl", "mmusculus_gene_ensembl")
    goSets <- getBM(c("ensembl_gene_id", "go_id"), mart = mart,
                    filters = "ensembl_gene_id", values = rownames(res))
    goSets <- goSets[!nchar(goSets$go_id) == 0, ]
    goSets <- with(goSets, split(go_id, ensembl_gene_id))
    save(goSets, file = goset_data)
} else {
   load(goset_data)
}
